### 2019-03-21 outline/outline.tex
Change outline

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[format=plain, font=it]{caption}
\usepackage{mathpazo}
\usepackage{biblatex}

@@

\begin{titlepage} % Suppresses displaying the page number on the title page and the subsequent page counts as page 1
	\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for horizontal lines, change thickness here
	\center

	\textsc{\LARGE University of Minnesota}\\[0.35cm]
	\textsc{\Large SENG 5852}\\[1.5cm]

	{\huge\bfseries The Race to Continuous Integration, Delivery, \& Deployment}\\[0.35cm]	
	\textsc{\Large Research Paper Outline}\\[1cm]

	\textsc{\large\author
		LLue Xiong\\
	}

	\vfill\vfill\vfill
	\large\today
	\vfill
\end{titlepage}

@@

\subsection{Thesis Statement}
The software industry is transforming at a rapid pace to accommodate the dynamic nature of the market and as a result, it continues to struggle to find process-identity with continuous software development.

\subsection{Purpose Statement}
Software engineering has for two decades, contemplated and experimented with the concept of distributing software faster and better, without sacrificing reliability and security. There is a widespread movement in the technical community to advocate for using Agile practices to achieve such a feat, and in particular: continuous integration, delivery, and deployment. The traditional methods of software development no longer meets the need of businesses that want to proactively engage and retain customers. The organizational transition to Agile practices demands a large mentality change, understanding software as small increments developed with cross-collaboration of small team units as opposed to large modules developed by extensive siloed units.

\section{Body}
	\subsection{Differences of Interpretation \& Implementation}
	\subsection{What is Continuous Integration, Delivery, \& Deployment}
		\subsubsection{Inherently Agile}
		\subsubsection{Continuous Integration}
		\subsubsection{Continuous Delivery}
		\subsubsection{Continuous Deployment}
	\subsection{Struggles of Traceability}
	\subsection{Paradigm Shift in Leadership}
	naturally forming resistance from individuals from within.

\section{Conclusion}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage[format=plain, font=it]{caption}
\usepackage{mathpazo}
\usepackage{biblatex}

@@

\begin{titlepage} % Suppresses displaying the page number on the title page and the subsequent page counts as page 1
	\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for horizontal lines, change thickness here
	\center
	\textsc{\LARGE University of Minnesota}\\[0.35cm]
	\textsc{\Large SENG 5852}\\[1.5cm]
	{\huge\bfseries Continuous Integration, Delivery, \& Deployment: Transforming the Software Industry}\\[0.35cm]	
	\textsc{\Large Outline}\\[1cm] 
	\textsc{\large\author
		LLue Xiong\\
	}
	\vfill\vfill\vfill
	\large\today
	\vfill
\end{titlepage}

@@

\subsection{Thesis Statement}
The software industry is transforming at a rapid pace to accommodate the dynamic nature of the market and as a result, it continues to struggle to find process-identity with continuous software engineering.

\subsection{Purpose Statement}
Software engineering has for two decades, experimented with the concept of distributing software in faster release cycles; endeavoring to do so without sacrificing reliability and security. To achieve such a goal, there has been a widespread movement in the technical community to advocate for using Agile practices, and in particular: continuous integration, delivery, and deployment. The traditional methods of software development no longer meet the need of businesses that -- now more than ever -- want to proactively engage and retain their customers. The organizational transition to Agile practices demands a large mentality change and require individuals to recognize software as incremental features developed with cross-collaboration of small comprehensive team units, as opposed to large modules developed by siloed units.

\section{Body}
	\subsection{What is Continuous Integration, Delivery, \& Deployment}
		\subsubsection{Inherently Agile}
		\begin{itemize}[noitemsep]
			\item What is Agile? 
			\item What are the core ideas of Agile?
			\item How does Agile tie in with CI/CDE/CD?
		\end{itemize}
		\vspace{-7mm}
		\subsubsection{Continuous Integration}
		\begin{itemize}[noitemsep]
			\item What does CI mean?
		\end{itemize}
		\subsubsection{Continuous Delivery}
		\begin{itemize}[noitemsep]
			\item What does CDE mean?
		\end{itemize}
		\subsubsection{Continuous Deployment}
		\begin{itemize}[noitemsep]
			\item What does CD mean?
		\end{itemize}

	\subsection{Differences of Interpretation \& Implementation}
		\subsubsection{Viewpoint of Software Professionals}
		\begin{itemize}[noitemsep]
			\item How do software professionals interpret and implement CI/CD/CDE?
		\end{itemize}
		\subsubsection{Viewpoint of Academic Researchers}
		\begin{itemize}[noitemsep]
			\item How do academic researchers interpret and believe how CI/CD/CDE should be implemented?
		\end{itemize}
		\subsubsection{Collaboration Effort}
		\begin{itemize}[noitemsep]
			\item What effort is there to bridge the phenomena of non-collaboration between developers and researchers?
		\end{itemize}

	\subsection{Benefits of Continuous Integration, Delivery, \& Deployment}
		\subsubsection{Self-healing Systems}
		\begin{itemize}[noitemsep]
			\item What are the metrics and tools that software professionals use to mitigate having to manually fix software issues?
			\item How do these self-healing systems work?
		\end{itemize}
		\subsubsection{Reduce Risk}
		\begin{itemize}[noitemsep]
			\item How does continuous software engineering reduces risk in systems?
		\end{itemize}
		\subsubsection{Faster Release Cycles}
		\begin{itemize}[noitemsep]
			\item How are faster release cycles are achieved?
		\end{itemize}
		\subsubsection{Overall Cost Reduction}
		\begin{itemize}[noitemsep]
			\item Why will all of the above will reduce cost?
		\end{itemize}

	\subsection{Struggles of Traceability}
		\subsubsection{Importance}
		\begin{itemize}[noitemsep]
			\item What is the importance of traceability for the software engineering community?
		\end{itemize}
		\subsubsection{Problem of Mapping}
		\begin{itemize}[noitemsep]
			\item What is the problem of mapping requirements to implemented code and the converse?
		\end{itemize}
		\subsubsection{Eiffel Framework}
		\begin{itemize}[noitemsep]
			\item What is the proposed solution to address traceability issues in CI/CDE/CD environments?
		\end{itemize}

	\subsection{Transition an Agile Environment}
		\subsubsection{The Effect of Organizational Change to Agile}
		\begin{itemize}[noitemsep]
			\item What are the problems that businesses face in attempt to switch to Agile practices?
		\end{itemize}
		\subsubsection{Roles in Agile}
		\begin{itemize}[noitemsep]
			\item What are typical roles that each individual plays in an Agile environment? 
			\item Why do these roles exist?
		\end{itemize}
		\subsubsection{Paradigm Shift in Leadership}
		\begin{itemize}[noitemsep]
			\item How has leadership changed as a result of Agile?
		\end{itemize}

\section{Conclusion}
	\subsection{Rephrase Thesis Statement}
	\subsection{Closing Statement}
